
# Results

```{r resultsText}

inc_spp <- dat_summary |>
  dplyr::filter(trend == "increase") |>
  dplyr::pull(Common)

dec_spp <- dat_summary |>
  dplyr::filter(trend == "decrease") |>
  dplyr::pull(Common)

```

## Overall

There were `r nrow(dat_summary)` different species recorded across the `r length(unique(dat$year))` years with data. The most common species was `r dat_summary |> dplyr::filter(records == max(records)) |> dplyr::pull(Common)` with `r dat_summary |> dplyr::filter(records == max(records)) |> dplyr::pull(records)` records.

`r length(inc_spp) |> envFunc::numbers2words() |> stringr::str_to_sentence()` species appeared to increase over the years of the study`r if(length(inc_spp)) paste0(" (", envFunc::vec_to_sentence(inc_spp), ")")`, while `r length(dec_spp) |> envFunc::numbers2words()` species showed a decrease`r if(length(dec_spp)) paste0(" (", envFunc::vec_to_sentence(dec_spp), ")")`.

The table below shows the:

* species recorded
* total number of records for a species
* number of years in which a species was recorded; and
* the number of cells in which a species was recorded
* guestimate of trend for the species, based on a linear model fitted to the number of cells by year

Each cell was `r ras_res` by `r ras_res` metres.

Below the table is a map showing where all records were taken.

```{r tabCellCount}

DT::datatable(dat_summary |>
                dplyr::mutate(Common = paste0("<a href='#", gsub("\\s", "-", tolower(Common)), "'>", Common, "</a><br>")) |>
                dplyr::select(Common, records, years, cells, trend)
              , caption = "Species recorded and their total records, years with a record, cells with a record and trend estimate"
              , escape = FALSE
              )

```

<br>

```{r map, fig.cap = "Map of all records"}

tm_shape(dat_sf) +
  tm_dots(col = "year"
          , palette = "plasma"
          ) +
  tm_scale_bar()

```

## By species

```{r sp_rmd}

  sp_rmd <- NULL

  # this loops through sp_rmd.Rmd,

  for (i in sort(unique(dat$Species))) {
    
    spID <- i
    
    sp_rmd <- c(sp_rmd, knit_expand(fs::path(here::here()
                                           , "child"
                                           , "sp.Rmd"
                                           )
                                  )
               )
    
  }

```

`r paste(knit(text = sp_rmd), collapse = '\n')`
