
# Results

## Overall

The table below shows the:

* species recorded
* total number of records for a species
* number of years in which a species was recorded; and
* the number of cells in which a species was recorded.

Each cell was `r ras_res` by `r ras_res` metres.

There were `r nrow(dat_summary)` different species recorded across the `r length(unique(dat$year))` years with data. The most common species was `r dat_summary |> dplyr::filter(records == max(records)) |> dplyr::pull(Common)` with `r dat_summary |> dplyr::filter(records == max(records)) |> dplyr::pull(records)` records.

Below the table is a map showing where records were taken.

```{r tabCellCount}

DT::datatable(dat_summary |>
               dplyr::select(Common, records, years, cells)
             )

```

```{r map}

tm_shape(dat_sf) +
  tm_dots(col = "year"
          , palette = "plasma"
          ) +
  tm_scale_bar()

```

## By species

```{r sp_rmd}

  sp_rmd <- NULL

  # this loops through sp_rmd.Rmd,

  for (i in sort(unique(dat$Species))) {
    
    spID <- i
    
    sp_rmd <- c(sp_rmd, knit_expand(fs::path(here::here()
                                           , "child"
                                           , "sp.Rmd"
                                           )
                                  )
               )
    
  }

```

`r paste(knit(text = sp_rmd), collapse = '\n')`
